New modal operators for constructive mathematics

### 2023-05-02 slides-luminy2023.tex
Slides finished

\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\M}{\mathcal{M}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\BB}{\mathbb{B}}
\newcommand{\pp}{\mathbbm{p}}
\newcommand{\MM}{\mathbb{M}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\FF}{\mathbb{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\GG}{\mathbb{G}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\K}{\mathcal{K}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\TT}{\mathbb{T}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\aaa}{\mathfrak{a}}
\newcommand{\ccc}{\mathfrak{c}}
\newcommand{\ppp}{\mathfrak{p}}
\newcommand{\fff}{\mathfrak{f}}
\newcommand{\mmm}{\mathfrak{m}}
\newcommand{\defeq}{\vcentcolon=}
\newcommand{\defeqv}{\vcentcolon\equiv}
\newcommand{\Sh}{\mathrm{Sh}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Zar}{\mathrm{Zar}}
\newcommand{\op}{\mathrm{op}}
\newcommand{\Set}{\mathrm{Set}}
\newcommand{\Eff}{\mathrm{Ef{}f}}
\newcommand{\Sch}{\mathrm{Sch}}
\newcommand{\Aff}{\mathrm{Aff}}
\newcommand{\Ring}{\mathrm{Ring}}
\newcommand{\LocRing}{\mathrm{LocRing}}
\newcommand{\LRS}{\mathrm{LRS}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\Spec}{\mathrm{Spec}}
\newcommand{\lra}{\longrightarrow}
\newcommand{\RelSpec}{\operatorname{Spec}}
\renewcommand{\_}{\mathpunct{.}}
\newcommand{\?}{\,{:}\,}
\newcommand{\speak}[1]{\ulcorner\text{\textnormal{#1}}\urcorner}
\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\affl}{\ensuremath{{\ul{\ensuremath{\AA}}^1}}}
\newcommand{\Ll}{\text{iff}}
\newcommand{\inv}{inv.\@}
\newcommand{\seq}[1]{\mathrel{\vdash\!\!\!_{#1}}}
\newcommand{\hg}{\mathbin{:}}  % homogeneous coordinates

@@

\setbeamersize{text margin left=2.0em,text margin right=2.0em}

@@

  Ingo Blechschmidt
  \par
\end{frame}}

@@

  \textbf{Def.} For a predicate~$P$ on finite lists over a set~$X$, inductively
  define:
  \[
    \infer{P \,|\, \sigma}{P(\sigma)}
    \qquad
    \infer{P \,|\, \sigma}{\forall(x \in X)\_\ P \,|\, \sigma x}
  \]

  \textbf{Def.} A preorder is \hil{well} iff~$\mathsf{Good} \,|\, [\,]$, where
  $\mathsf{Good}(\sigma) \defeqv (\exists(i < j)\_ \sigma[i] \leq \sigma[j])$.
\end{frame}}

@@

  \textbf{Prop.} Let~$(X,{\leq})$ be preorder. Let~$x < y$ mean~$x \leq y \wedge \neg(y \leq x)$. \\
  Then: If~$X$ is well$^\star$, then~$({<})$ is well-founded$^\star$.

  \emph{Proof.} An infinite strictly descending chain would also be good. \qed

@@

\begin{frame}{Maximal ideals}
  \only<1-7>{\textbf{Thm.}
  Let~$M$ be a surjective matrix with more rows than columns over a
  ring~$A$. Then~$1 = 0$ in~$A$.

@@

  \only<4-7>{\bigskip\par\centering\scalebox{0.9}{\begin{tikzpicture}
    \node (0) at (0,1) {$(0) = \{0\}$};
    \node (1) at (0,5) {$(1) = \ZZ$};
    \node (2) at (-2,4) {$(2)$};
    \node [right of=2] (3) {$(3)$};
    \node [below of=2] (4) {$(4)$};
    \node [below of=2, xshift=0.7cm] (6) {$(6)$};
    \node [right of=3] (5) {$(5)$};
    \node [right of=5] (7) {$(7)$};
    \node [right of=7] (7d) {$\ldots$\phantom{(}};
    \node [right of=7d, xshift=3cm, yshift=-2cm] (max)
    {\vbox{\small\it maximal among the proper ideals \\ \medskip $\neg(1 \in
    \mmm)$ \\ \medskip $x \in \mmm \quad\vee\quad 1 \in \mmm + (x)$}};
    \node [below of=4] (8) {$(8)$};
    \node [right of=8, xshift=3cm] (8d) {$\ldots$};
    \draw (0) -- (8);
    \draw (0) -- (8d);
    \draw (0) -- (6);
    \draw (2) -- (1);
    \draw (3) -- (1);
    \draw (5) -- (1);
    \draw (7) -- (1);
    \draw (7d) -- (1);
    \draw (4) -- (2);
    \draw (8) -- (4);
    \draw (6) -- (2);
    \draw (6) -- (3);
    \draw [mypurple!30, thick, shorten <=-2pt, shorten >=-2pt, ->] (max) to [out=120, in=-30] (7d);
    \begin{pgfonlayer}{background}
      \draw[decorate, very thick, draw=mypurple!30]
        ($(2.south west) + (8pt, 0)$) arc(270:180:8pt) --
        ($(2.north west) + (0, -8pt)$) arc(180:90:8pt) --
        ($(7d.north east) + (-8pt, 0)$) arc(90:0:8pt) --
        ($(7d.south east) + (0, 8pt)$) arc(0:-90:8pt) --
        cycle;
    \end{pgfonlayer}
  \end{tikzpicture}}\par}

@@

  Let~$A$ be a ring. \emph{Does there exist a maximal ideal~$\mmm \subseteq A$?}
  \pause
  \begin{enumerate}
    \item \good{Yes}, if \bad{Zorn's lemma} is available.
    \medskip
    \pause

@@

    \item \good{Yes}, if~$A$ is countable (irrespective of membership decidability):
    {\footnotesize\begin{align*}
      \mmm_0 &= \{ 0 \}, &
      \mmm_{n+1} &= \mmm_n + (\underbrace{\{ x \in A \,|\, x = x_n \wedge
        1 \not\in \mmm_n + (x_n) \}}_{\text{a certain subsingleton set}})
    \end{align*}}
    \vspace*{-0.5em}
    \pause

    \item In the general case: \bad{No}, but we \good{do have} the first-order
    consequences of the existence of a maximal ideal.
  \end{enumerate}
\end{frame}

@@

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\includegraphics[width=\paperwidth]{eventually-monad}\end{minipage}}
\begin{frame}
  \vspace*{\paperheight}\vspace*{-3.4em}\centering
  \emph{Agda formalization available.}
\end{frame}}

>>>>

\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\M}{\mathcal{M}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\BB}{\mathbb{B}}
\newcommand{\pp}{\mathbbm{p}}
\newcommand{\MM}{\mathbb{M}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\FF}{\mathbb{F}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\GG}{\mathbb{G}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\K}{\mathcal{K}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\TT}{\mathbb{T}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\renewcommand{\P}{\mathcal{P}}
\newcommand{\aaa}{\mathfrak{a}}
\newcommand{\ccc}{\mathfrak{c}}
\newcommand{\ppp}{\mathfrak{p}}
\newcommand{\fff}{\mathfrak{f}}
\newcommand{\mmm}{\mathfrak{m}}
\newcommand{\defeq}{\vcentcolon=}
\newcommand{\defeqv}{\vcentcolon\equiv}
\newcommand{\Sh}{\mathrm{Sh}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Zar}{\mathrm{Zar}}
\newcommand{\op}{\mathrm{op}}
\newcommand{\Set}{\mathrm{Set}}
\newcommand{\Eff}{\mathrm{Ef{}f}}
\newcommand{\Sch}{\mathrm{Sch}}
\newcommand{\Aff}{\mathrm{Aff}}
\newcommand{\Ring}{\mathrm{Ring}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\LocRing}{\mathrm{LocRing}}
\newcommand{\LRS}{\mathrm{LRS}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\Spec}{\mathrm{Spec}}
\newcommand{\lra}{\longrightarrow}
\newcommand{\RelSpec}{\operatorname{Spec}}
\renewcommand{\_}{\mathpunct{.}}
\newcommand{\?}{\,{:}\,}
\newcommand{\speak}[1]{\ulcorner\text{\textnormal{#1}}\urcorner}
\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\affl}{\ensuremath{{\ul{\ensuremath{\AA}}^1}}}
\newcommand{\Ll}{\text{iff}}
\newcommand{\inv}{inv.\@}
\newcommand{\seq}[1]{\mathrel{\vdash\!\!\!_{#1}}}
\newcommand{\hg}{\mathbin{:}}  % homogeneous coordinates

@@

\setbeamersize{text margin left=1.60em,text margin right=1.60em}

@@

  Ingo Blechschmidt \\
  j.w.w. Alexander Oldenziel
  \par
\end{frame}}

@@

  \textbf{Def.} For a predicate~$P$ on finite lists over a set~$X$, inductively
  define:
  \[
    \infer{P \,|\, \sigma}{P\sigma}
    \qquad
    \infer{P \,|\, \sigma}{\forall(x \in X)\_\ P \,|\, \sigma x}
  \]

  \textbf{Def.} A preorder is \hil{well} iff~$\mathsf{Good} \,|\, [\,]$, where
  $\mathsf{Good}\,\sigma \defeqv (\exists(i < j)\_ \sigma[i] \leq \sigma[j])$.
\end{frame}}

@@

  \textbf{Prop.} Let~$(X,{\leq})$ be preorder. Let~``$x < y$'' mean~$x \leq y \wedge \neg(y \leq x)$. \\
  Then: If~$X$ is well$^\star$, then~$({<})$ is well-founded$^\star$.

  \emph{Proof.} An infinite strictly descending chain would also be good. \qed
  \pause

@@

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\vspace*{5.95cm}\includegraphics[width=\paperwidth]{fr1}\end{minipage}}
\begin{frame}{Maximal ideals}
  \only<1-7>{\textbf{Thm.}
  Let~$M$ be a surjective matrix with more rows than columns over a
  ring~$A$. Then~$1 = 0$ in~$A$.

@@

  \only<4-7>{\bigskip\par\centering\scalebox{0.9}{\centering\begin{tikzpicture}
    \node (0) at (0,1) {$(0) = \{0\}$};
    \node (1) at (0,5) {$(1) = \ZZ$};
    \node (2) at (-2,4) {$(2)$};
    \node [right of=2] (3) {$(3)$};
    \node [below of=2] (4) {$(4)$};
    \node [below of=2, xshift=0.7cm] (6) {$(6)$};
    \node [right of=3] (5) {$(5)$};
    \node [right of=5] (7) {$(7)$};
    \node [right of=7] (7d) {$\ldots$\phantom{(}};
    \node [right of=7d, xshift=3cm, yshift=-2cm] (max)
    {\vbox{\small\it maximal among the proper ideals \\ \medskip $\neg(1 \in
    \mmm)$ \\ \medskip $x \in \mmm \quad\vee\quad 1 \in \mmm + (x)$}};
    \node [below of=4] (8) {$(8)$};
    \node [right of=8, xshift=3cm] (8d) {$\ldots$};
    \draw (0) -- (8);
    \draw (0) -- (8d);
    \draw (0) -- (6);
    \draw (2) -- (1);
    \draw (3) -- (1);
    \draw (5) -- (1);
    \draw (7) -- (1);
    \draw (7d) -- (1);
    \draw (4) -- (2);
    \draw (8) -- (4);
    \draw (6) -- (2);
    \draw (6) -- (3);
    \draw [mypurple!30, thick, shorten <=-2pt, shorten >=-2pt, ->] (max) to [out=120, in=-30] (7d);
    \begin{pgfonlayer}{background}
      \draw[decorate, very thick, draw=mypurple!30]
        ($(2.south west) + (8pt, 0)$) arc(270:180:8pt) --
        ($(2.north west) + (0, -8pt)$) arc(180:90:8pt) --
        ($(7d.north east) + (-8pt, 0)$) arc(90:0:8pt) --
        ($(7d.south east) + (0, 8pt)$) arc(0:-90:8pt) --
        cycle;
    \end{pgfonlayer}
  \end{tikzpicture}\par}\par}

@@

  Let~$A$ be a ring. \emph{Does there exist a maximal ideal~$\mmm \subseteq A$?}
  \pause
  \begin{enumerate}
    \item \good{Yes}, if \bad{Zorn's lemma} is available.
    \bigskip
    \pause

@@

    \item \good{Yes}, if~$A$ is countable (irrespective of membership decidability):
    {\footnotesize\begin{align*}
      \mmm_0 &= \{ 0 \}, &
      \mmm_{n+1} &= \mmm_n + (\underbrace{\{ x \in A \,|\, x = x_n \wedge
        1 \not\in \mmm_n + (x_n) \}}_{\text{a certain subsingleton set}})
    \end{align*}}
    \vspace*{4.5em}
    \visible<11>{{
      \centering
      \raisebox{0pt}[0pt][0pt]{
        \hspace*{1.5em}
        \begin{tikzpicture}
          \node (inner) at (17.3mm,-20mm) {\textit{``a bad joke''}};
          \path (0,0) pic{laurel-wreath};
        \end{tikzpicture}
        \hspace*{-3em}
        \begin{tikzpicture}
          \node (inner) at (17.5mm,-18mm) {\vbox{\small\centering\textit{``non- \\informative''}}};
          \path (0,0) pic{laurel-wreath};
        \end{tikzpicture}
      }
      \par
    }}
    \pause
    \pause
    \vspace*{-4.5em}

    \item In the general case: \bad{No}, but the \emph{first-order
    consequences} of the existence of a maximal ideal \good{do hold}.
  \end{enumerate}
\end{frame}}

\begin{frame}{Questions}
  \begin{enumerate}
    \item \!Why was the inductive revolution so powerful?
    \bigskip

    \item \!Why do proofs using Zorn's maximal ideals work so well in constructive algebra?
    \bigskip

    \item \!Why are elements of~$\bigcap_\ppp \ppp$ not necessarily nilpotent?
    \bigskip

    \item How can we extract computational content from classical proofs?
  \end{enumerate}
\end{frame}

\renewcommand{\insertframeextra}{a}
{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\vspace*{3.23cm}\includegraphics[width=\paperwidth]{topos-horses-lighter-lighter}\end{minipage}}
\begin{frame}{Constructive forcing (= Grothendieck toposes)}
  \justifying
  Let~$L$ be a \hil{forcing notion}, a preorder equipped
  with a \hil{covering system}.\only<1-2>{\footnote{\scriptsize A covering system consists of a
  set~$\Cov(\sigma) \subseteq P({\downarrow}\sigma)$ of \emph{coverings} for
  each element~$\sigma \in L$ subject only to the following simulation
  condition: If~$\tau \preccurlyeq \sigma$ and~$R \in \Cov(\sigma)$, there
  should be a covering~$S \in \Cov(\tau)$ such that~$S \subseteq
  {\downarrow}R$.}}\only<3->{\textsuperscript{\phantom{1}}}
  \hil{Filters}~$F \subseteq L$ are subsets which are upward-closed,
  downward-directed and split the covering system.\only<1-2>{\footnote{\scriptsize
  A subset~$F$ splits the covering system iff for every~$\sigma \in L$ and~$R \in \Cov(\sigma)$,
  if~$\sigma \in F$, then~$\tau \in F$ for some~$\tau \in R$.}}\only<3>{\textsuperscript{\phantom{2}}}
  \pause

  {\centering\footnotesize\begin{tabular}{lll}
    \toprule
    preorder~$L$ & coverings of an element~$\sigma \in L$ & filters of~$L$ \\
    \midrule
    $X^*$ & $\{ \sigma x \,|\, x \in X \}$ & maps~$\NN \to X$ \\
    $X^*$ & $\{ \sigma x \,|\, x \in X \}$,\ \
    $\{ \sigma\tau \,|\, \tau \in X^*, a \in \sigma\tau \}$ for each~$a \in X$ & surjections~$\NN \twoheadrightarrow X$ \\
    f.g. ideals & --- & ideals \\
    f.g. ideals & $\{ \sigma+(a), \sigma+(b) \}$ for each~$ab \in \sigma$,\ \
    $\{\}$ if~$1 \in \sigma$ & prime ideals \\
    opens & $\mathcal{U}$ such that~$\sigma = \bigcup \mathcal{U}$ & points \\
    $\{\star\}$ & $\{ \star \,|\, \varphi \} \cup \{ \star \,|\, \neg\varphi \}$ &
    witnesses of~\textsc{lem}
    \\
    \bottomrule
  \end{tabular}\par}
  \bigskip

  \only<3>{\textbf{Def.} Given a monotone predicate~$P$
  on~$L$, inductively define:
  \[
    \infer{P \,|\, \sigma}{P\sigma}
    \qquad
    \infer[{\small(R \in \Cov(\sigma))}]{P \,|\, \sigma}{\forall(\tau \in R)\_\ P \,|\, \tau}
  \]
  We use quantifier-like notation: ``$\nabla\sigma\_ P\sigma$'' means~$P \,|\, \sigma$.}
\end{frame}}

\addtocounter{framenumber}{-1}
\renewcommand{\insertframeextra}{b}
{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\vspace*{3.23cm}\includegraphics[width=\paperwidth]{topos-horses-lighter-lighter}\end{minipage}}
\begin{frame}{Constructive forcing (= Grothendieck toposes)}
  A forcing notion is a template for a \hil{forcing extension}~$V^\nabla$
  of the base universe~$V$:

  \begin{center}\begin{tikzpicture}[remember picture,overlay]
    \node[thick, draw=mypurpledark, rectangle, inner sep=0.3em] (kj) {
      \begin{minipage}{0.6\textwidth}
        \centering
        \emph{When we say that a statement \hil{holds in~$V^\nabla$},} \\
        we mean that its~$\nabla$-translation is true.\par
        \vspace*{0.3em}
      \end{minipage}
    };
  \end{tikzpicture}\end{center}
  \bigskip
  \pause

  \textbf{Examples.}
  \begin{enumerate}
  \justifying
  \item For~$L = \{\star\}$, ``every number is zero or a successor'' holds
  in~$V^\nabla$ because

  \vspace*{-1em}
  \[ \forall(n \in \NN)\_ \neg\neg\bigl(\neg\neg(n = 0) \vee
    \neg\neg(\exists(m \in \NN)\_ \neg\neg(n = S(m)))\bigr). \]

  \pause
  \item For~$L$ associated to a space, ``every symmetric matrix has an
  eigenvector'' holds in~$V^\nabla$ iff for every continuous family of
  symmetric matrices, locally there is a continuous eigenvector-picking
  function.
  \pause
  \medskip

  \item For any~$L$, ``there is a filter of~$L$'' holds in~$V^\nabla$,
  witnessed by the \hil{generic filter} of~$L$.
  \pause
  \medskip

  \item Let~$X$ be a preorder. Then:

  \hil{$\blacktriangleright$} $X$ is well iff the generic sequence~$\NN \to X$
  is good.

  \hil{$\blacktriangleright$} $({<})$ is well-founded iff the generic strictly
  descending chain validates~$\bot$.
  \end{enumerate}
\end{frame}}

\renewcommand{\insertframeextra}{}
\begin{frame}{The modal multiverse}
  \only<1-2>{In general, ``$\varphi$ holds in~$V^\nabla$'' and~``$\varphi$ holds in~$V$''
  are \emph{not} equivalent.

  \hil{$\blacktriangleright$}
  For \hil{positive} extensions, they are equivalent for coherent implications.\\
  %\footnote{bounded first-order formulas of the
  %form~$\forall\ldots\forall\_(\ldots\Rightarrow\ldots)$,
  %where antecedent and succedent do not contain~``$\forall$''
  %and~``${\Rightarrow}$''}.
  \phantom{\hil{$\blacktriangleright$}} {\footnotesize -- e.g. the ``Barr cover''.\par}

  \hil{$\blacktriangleright$}
  For \hil{positive open} extensions, they are equivalent for bounded first-order formulas. \\
  \phantom{\hil{$\blacktriangleright$}} {\footnotesize -- e.g. $V^\nabla$ containing
  the generic surjection~$\NN \twoheadrightarrow X$, if~$X$ is inhabited.\par}
  \bigskip}
  \pause

  \textbf{Def.} A statement~$\varphi$ holds \ldots
  \begin{enumerate}
    \small
    \item[$\blacktriangleright$] \hil{everywhere} ($\necessary\varphi$) iff
    it holds in every extension.
    \item[$\blacktriangleright$] \hil{somewhere} ($\possible\varphi$) iff
    it holds in some positive extension.
    \item[$\blacktriangleright$] \hil{proximally} ($\xpossible\varphi$) iff
    it holds in some positive overt extension.
  \end{enumerate}
  \bigskip
  \pause

  \small
  \begin{multicols}{2}
    For every set~$X$, \emph{proximally} \\
    there is an enumeration~$\NN \twoheadrightarrow X$.

    A preorder is well iff \emph{everywhere}, \\
    every sequence is good.

    A ring element is nilpotent iff \\
    all prime ideals \emph{everywhere} contain it.

    For every ring, \emph{proximally} \\ there is a maximal ideal.

    A relation is well-founded iff \emph{everywhere}, there is no descending chain.

    \emph{Somewhere}, \\ the law of excluded middle holds.
  \end{multicols}
\end{frame}

\begin{frame}{The multiverse perspective}
  \begin{enumerate}
    \item \!\emph{Why was the inductive revolution so powerful?}

    Because the inductive conditions
    are equivalent to truth in \emph{all} forcing extensions.
    \bigskip

    \item \!\emph{Why do proofs using Zorn's maximal ideals work so well in constructive algebra?}

    Because every ring proximally has a maximal ideal.
    \bigskip

    \item \!\emph{Why are elements of~$\bigcap_\ppp \ppp$ not necessarily nilpotent?}

    Because we forgot the prime ideals in forcing extensions.
    \bigskip

    \item \emph{How can we extract computational content from classical proofs?}

    By traveling the multiverse (upwards, keeping ties to the base), exploiting
    that \\
    -- \textsc{lem} holds \emph{somewhere} and \\
    -- \textsc{dc} holds \emph{proximally}.
  \end{enumerate}
\end{frame}

@@

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\includegraphics[width=\paperwidth]{eventually-monad-cropped}\end{minipage}}
\begin{frame}
  \vspace*{\paperheight}\vspace*{-2.05em}\centering
  \emph{Agda formalization available.}
\end{frame}}
